\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-23 paper.tex
3.3

For \textit{admitted} demands (including the newly admitted one), we carry out traffic scheduling to further optimize the bandwidth allocation periodically (e.g., every 10 minutes).
We model this as a linear programming problem, which maximizes the overall availability to be achieved (in a probabilistic sense), under the constraint that all bandwidth target must be met. Specifically,

@@

For a s-d pair $k$ of BA demand $d$, we use $R_{dk}^{\mathbf{z}}$ to denote the ratio of the effective bandwidth to the demanded bandwidth under network scenario $\mathbf{z}$, which is defined as:
 \begin{eqnarray} \label{R2}
R_{dk}^{\mathbf{z}}=\frac{\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d}, \quad \forall  d \in \hat{D}, k \in K, \mathbf{z}\in Z.
\end{eqnarray}
%Figure \ref{Time-fig} gives an illustration on resource allocation return.
%For a given bandwidth allocation vector, it plots the sorted return and the corresponding probability.
%$R_{dk}^{\mathbf{z}}$ describes the allocation return under network scenario $\mathbf{z}$.
Here, our consideration is tunnel $t$ might be unavailable (i.e., $v_t^{\mathbf{z}} =0$) under a network scenario, but if $R_{dk}^{\mathbf{z}} \ge 1$ holds, then this scenario is still \textit{qualified}. 
%If for every source-destination pair $k$, the total reserved bandwidth through all available tunnels is larger than $\mathbf{b}^k_d$, then the bandwidth demand can still be satisfied, and network scenario $\mathbf{z}$ can be regarded as \textit{qualified}, i.e., 
%$R_{dk}^{\mathbf{z}} \ge 1, \forall k \in K$.
To meet the availability target, we should guarantee the total probability of the qualified scenarios 
is no less than the availability target, i.e., $\sum_{R_{dk}^{\mathbf{z}} \ge 1} p_{\mathbf{z}} \ge \beta_d$.
%for each s-d pair $k$ of demand $d$.
%$\forall d \in \hat{D}, k \in K$.
%This is a step function and we define the following potential function:
% 
%  \begin{eqnarray} \label{B3}
%\sum_{R_{dk}^{\mathbf{z}} \ge 1} p_{\mathbf{z}} \ge \beta_i, \forall d \in \hat{D}
%\end{eqnarray}
%$R_{dk}^{\mathbf{z}}$ is the ratio of allocated bandwidth to  demand over node pair $k$ under network scenario $\mathbf{z}$.
However, this condition will result in an mixed interger linear programming problem, 
and we choose to relax it and sovle a linear programming problem.

@@

Besides, the bandwidth allocation result $\{f_{d}^t}$ should be non-negative and limited by the network capacity, i.e.,
\begin{equation}
f_{d}^t \ge 0, \quad\forall d \in D ,  k\in K,   t\in T_{k}.
\label{constraint-f2}
\end{equation}
%Then total traffic through link $e$ should not be larger than its capacity $c_e$:
and
\begin{equation}
 \sum_{d \in \hat{D}}\ \sum_{k\in K, t\in T_{k}}f_{d}^tu_t^e \le c_e, \quad \forall e \in E.
\label{constraint-e2}
\end{equation}

Finally, our traffic scheduling will minimize the overall bandwith allocated to all admitted demands 
under the above constraints, i.e., 
%thus,  we can finally give the formulation of traffic engineering formulation: 
\begin{equation}
\small
\begin{aligned} \label{BATE-TE}
% &maximize  \sum_{i\in I_a} \sum_{\mathbf{z}\in Z}B_d^{\mathbf{z}}\times p_{\mathbf{z}}\\
%&\begin{array}{r@{\quad}r@{}l@{\quad}l}
&minimize \sum_{d \in \hat{D}, k \in K, t \in T_k} f_d^t 
s.t. (\ref{constraint-f2}), (\ref{constraint-e2}), (\ref{Smaller}), (\ref{R2}), (\ref{B2}), (\ref{Achieved})
%\begin{cases}
% \sum_{d \in \hat{D}}\ \sum_{k\in K}\sum_{t\in T_{k}}f_{d}^tu_t^e \le c_e, &\text{$\forall e \in E $.}\\
%R_{dk}^{\mathbf{z}}=\frac{\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d} , &\text{$\forall  d \in \hat{D}, \mathbf{z}\in \mathbf{z},  k \in K$.}\\
%R_{dk}^{\mathbf{z}}>=B_d^{\mathbf{z}},&{\forall d \in \hat{D}, \mathbf{z} \in Z, k\in K.} \\
%\sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}} \ge \beta_{\gamma_{i}},&{\forall d \in \hat{D}} .\\
% \sum_{t\in T_{k}} f_{d}^t \le \mathbf{b}^k_d, &{  \forall d \in \hat{D}, k \in K}.\\
%f_{d}^t \ge 0,&{\forall d \in \hat{D} , \forall k\in K,\forall t\in T_{k}}.\\
%\end{cases}\\
\end{array}
\end{aligned}
\end{equation}

@@

Soving this LP problem directly is possible, but as it considers every possible network scenario, 
the complexity will increase exponentially with the network size.
%For example, we consider a small inter-DC WAN which contains 3 links and  5 events.
%Each link has $2^5=32$ states and the network includes $32^3=32768$ states in total. 
%In reality, network scale is much larger and  the states volume will increase exponentially.
For instance, the B4 topology \cite{B4} has 12 nodes and 38 links,
so there are totally $2^{38}$ network failure scenarios (when only link failures considered).
%The explosive network scenarios make it impossible to solve $\mathsf{BATE}$ problem.
Therefore, an important question is how to effectively reduce the problem size without 
affecting the result significantly. TEAVAR \cite{Teavar} prunes a scenario if its probability is smaller than a threshold. However, such a threshould is difficult to choose, and it still has to enumerate all 
possible scenarios. Instead, we use a much faster prunning method, 
where at most two concurrent link failures will be considered in our network scenarios, 
and all the remaining scenarios will be converted into one special \textit{unqualified} scenario. 
In this way, the set of scenarios $Z$ and the corresponding $\{p_\mathbf{z}\}$ can be efficiently computed.

\iffalse
This method is easy but the accuracy and efficiency tradeoff threshold is hard to decide.
A large threshold could significantly accelerate the algorithm since large amount of network scenarios are cut off, however, the accuracy might decrease.
Instead, we propose to cut off network failure scenarios in which \textit{concurrent link failure number} is larger than $l$.
We think this method is much more practical since most scenarios could hardly happen (e.g., more than two links fail simultaneously). 
Therefore, we can ignore these scenarios.
To provide an upper bound of the traffic engineering problem, we collapse all the pruned scenarios into a single scenario with probability equal to the sum of probabilities of the pruned scenarios and regard that scenario as an unsafe one.
%Figure \ref{pic-fig} depicts an example of a simple network with four links when $l=2$. 
%The root node denotes all
%links are available (i.e., $[1111]$). 
%The $i$-th layer denotes concurrent $i$ link failures could happen. 
%Network scenarios (red) located in layer 3, 4 are pruned (the root node is regarded as layer 0).
%\begin{equation}
%\small
%\begin{aligned} \label{BATE-TE}
% &maximize  \sum_{i\in I} \sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}}\\
%&\begin{array}{r@{\quad}r@{}l@{\quad}l}
%s.t.
%\begin{cases}
% \sum_{d \in D}\ \sum_{\forall k\in K: t\in T_{k}}f_{d}^tu_t^e \le c_e, &\text{$\forall e \in E $.}\\
%R_{dk}^{\mathbf{z}}=\frac{\sum_{k\in K}\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d} , &\text{$\forall  d \in \hat{D}, \mathbf{z}\in \mathbf{z},  k \in K$.}\\
%R_{dk}^{\mathbf{z}}>=B_d^{\mathbf{z}},&{\forall d \in \hat{D}, \mathbf{z} \in Z, k\in K.} \\
%\sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}} \ge \beta_{\gamma_{i}},&{\forall d \in \hat{D}} .\\
% \sum_{t\in T_{k}} f_{d}^t \le \mathbf{b}^k_d, &{  \forall d \in \hat{D}, k \in K}.\\
%f_{d}^t \ge 0,&{\forall d \in \hat{D} , \forall k\in K: t\in T_{k}}.\\
%\end{cases}\\
%\end{array}
%\end{aligned}
%\end{equation}

@@

It is a step function and we can change it to the following linear format and we can also change it into a linear format:

>>>>

For \textit{admitted} demands (including the newly admitted ones), 
we carry out traffic scheduling to further optimize the bandwidth allocation periodically (e.g., every 10 minutes).
We model this as a linear programming problem, which maximizes the overall availability to be achieved (in a probabilistic sense), under the constraint that all bandwidth target must be met. Specifically,

@@

For an s-d pair $k$ of BA demand $d$, we use $R_{dk}^{\mathbf{z}}$ to denote the ratio of the effective bandwidth to the demanded bandwidth under network scenario $\mathbf{z}$, which is defined as:
 \begin{eqnarray} \label{R2}
R_{dk}^{\mathbf{z}}=\frac{\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d}, \quad \forall  d \in \hat{D}, k \in K, \mathbf{z}\in Z.
\end{eqnarray}
%Figure \ref{Time-fig} gives an illustration on resource allocation return.
%For a given bandwidth allocation vector, it plots the sorted return and the corresponding probability.
%$R_{dk}^{\mathbf{z}}$ describes the allocation return under network scenario $\mathbf{z}$.
Here, our consideration is tunnel $t$ might be unavailable (i.e., $v_t^{\mathbf{z}} =0$) under a network scenario, but if $R_{dk}^{\mathbf{z}} \ge 1$ holds, then this scenario is still \textit{qualified}. 
%If for every source-destination pair $k$, the total reserved bandwidth through all available tunnels is larger than $\mathbf{b}^k_d$, then the bandwidth demand can still be satisfied, and network scenario $\mathbf{z}$ can be regarded as \textit{qualified}, i.e., 
%$R_{dk}^{\mathbf{z}} \ge 1, \forall k \in K$.
To meet the availability target, we should guarantee the total probability of the qualified scenarios 
is no less than the availability target, i.e., $\sum_{R_{dk}^{\mathbf{z}} \ge 1} p_{\mathbf{z}} \ge \beta_d$.
%for each s-d pair $k$ of demand $d$.
%$\forall d \in \hat{D}, k \in K$.
%This is a step function and we define the following potential function:
% 
%  \begin{eqnarray} \label{B3}
%\sum_{R_{dk}^{\mathbf{z}} \ge 1} p_{\mathbf{z}} \ge \beta_i, \forall d \in \hat{D}
%\end{eqnarray}
%$R_{dk}^{\mathbf{z}}$ is the ratio of allocated bandwidth to  demand over node pair $k$ under network scenario $\mathbf{z}$.
However, this condition will result in an mixed interger linear programming problem, 
and we choose to relax it and sovle a linear programming problem.

@@

Besides, the bandwidth allocation result $f_{d}^t$ should be non-negative and limited by the network capacity, i.e.,
\begin{equation}
f_{d}^t \ge 0, \quad\forall d \in D ,  k\in K,   t\in T_{k}.
\label{constraint-f2}
\end{equation}
%Then total traffic through link $e$ should not be larger than its capacity $c_e$:
and
\begin{equation}
 \sum_{d \in \hat{D}}\ \sum_{k\in K, t\in T_{k}}f_{d}^tu_t^e \le c_e, \quad \forall e \in E.
\label{constraint-e2}
\end{equation}

Finally, our traffic scheduling will minimize the overall bandwith allocated to all admitted demands 
under the above constraints, i.e., 
%thus,  we can finally give the formulation of traffic engineering formulation: 
\begin{equation}
\small
\begin{aligned} \label{BATE-TE}
&minimize \sum_{d \in \hat{D}, k \in K, t \in T_k} f_d^t  \\
&\begin{array}{r@{\quad}r@{}l@{\quad}l}
s.t. (\ref{constraint-f2}), (\ref{constraint-e2}), (\ref{Smaller}), (\ref{R2}), (\ref{B2}), (\ref{Achieved})
%\begin{cases}
% \sum_{d \in \hat{D}}\ \sum_{k\in K}\sum_{t\in T_{k}}f_{d}^tu_t^e \le c_e, &\text{$\forall e \in E $.}\\
%R_{dk}^{\mathbf{z}}=\frac{\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d} , &\text{$\forall  d \in \hat{D}, \mathbf{z}\in \mathbf{z},  k \in K$.}\\
%R_{dk}^{\mathbf{z}}>=B_d^{\mathbf{z}},&{\forall d \in \hat{D}, \mathbf{z} \in Z, k\in K.} \\
%\sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}} \ge \beta_{\gamma_{i}},&{\forall d \in \hat{D}} .\\
% \sum_{t\in T_{k}} f_{d}^t \le \mathbf{b}^k_d, &{  \forall d \in \hat{D}, k \in K}.\\
%f_{d}^t \ge 0,&{\forall d \in \hat{D} , \forall k\in K,\forall t\in T_{k}}.\\
%\end{cases}\\
\end{array}
\end{aligned}
\end{equation}

@@

Solving this LP problem directly is possible, but as it considers every possible network scenario, 
the complexity will increase exponentially with the network size.
%For example, we consider a small inter-DC WAN which contains 3 links and  5 events.
%Each link has $2^5=32$ states and the network includes $32^3=32768$ states in total. 
%In reality, network scale is much larger and  the states volume will increase exponentially.
For instance, the B4 topology \cite{B4} has 12 nodes and 38 links,
so there are totally $2^{38}$ network failure scenarios (when only link failures considered).
%The explosive network scenarios make it impossible to solve $\mathsf{BATE}$ problem.
Therefore, an important question is \textit{how to effectively reduce the problem size without 
affecting the result significantly}. 
TEAVAR \cite{Teavar} prunes a scenario if its probability is smaller than a threshold. However, such a threshold is difficult to choose, and it still has to enumerate all 
possible scenarios. Instead, we use a much faster pruning method, 
where at most two concurrent link failures will be considered in our network scenarios, 
and all the remaining scenarios will be converted into one special \textit{unqualified} scenario. 
In this way, the set of scenarios $Z$ and the corresponding $\{p_\mathbf{z}\}$ can be efficiently computed.

\iffalse
This method is easy but the accuracy and efficiency tradeoff threshold is hard to decide.
A large threshold could significantly accelerate the algorithm since large amount of network scenarios are cut off, however, the accuracy might decrease.
Instead, we propose to cut off network failure scenarios in which \textit{concurrent link failure number} is larger than $l$.
We think this method is much more practical since most scenarios could hardly happen (e.g., more than two links fail simultaneously). 
Therefore, we can ignore these scenarios.
To provide an upper bound of the traffic engineering problem, we collapse all the pruned scenarios into a single scenario with probability equal to the sum of probabilities of the pruned scenarios and regard that scenario as an unsafe one.
\fi
%Figure \ref{pic-fig} depicts an example of a simple network with four links when $l=2$. 
%The root node denotes all
%links are available (i.e., $[1111]$). 
%The $i$-th layer denotes concurrent $i$ link failures could happen. 
%Network scenarios (red) located in layer 3, 4 are pruned (the root node is regarded as layer 0).
%\begin{equation}
%\small
%\begin{aligned} \label{BATE-TE}
% &maximize  \sum_{i\in I} \sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}}\\
%&\begin{array}{r@{\quad}r@{}l@{\quad}l}
%s.t.
%\begin{cases}
% \sum_{d \in D}\ \sum_{\forall k\in K: t\in T_{k}}f_{d}^tu_t^e \le c_e, &\text{$\forall e \in E $.}\\
%R_{dk}^{\mathbf{z}}=\frac{\sum_{k\in K}\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d} , &\text{$\forall  d \in \hat{D}, \mathbf{z}\in \mathbf{z},  k \in K$.}\\
%R_{dk}^{\mathbf{z}}>=B_d^{\mathbf{z}},&{\forall d \in \hat{D}, \mathbf{z} \in Z, k\in K.} \\
%\sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}} \ge \beta_{\gamma_{i}},&{\forall d \in \hat{D}} .\\
% \sum_{t\in T_{k}} f_{d}^t \le \mathbf{b}^k_d, &{  \forall d \in \hat{D}, k \in K}.\\
%f_{d}^t \ge 0,&{\forall d \in \hat{D} , \forall k\in K: t\in T_{k}}.\\
%\end{cases}\\
%\end{array}
%\end{aligned}
%\end{equation}

@@

It is a step function and we can change it to the following linear format :
